Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-22 article.tex
Modification taille imgs

    Therefore, the outcome of the method presented is a neighbouring graph, cf. Figure~\ref{fig:neigh_graph}, where each node is a \acrshort{bs} and each edge represent a neighbouring relationship between these two \acrshort{bs}s.
    \begin{figure}
        \centering
        \boxed{\includegraphics[width=2.5in]{images/illus_graphs/neighbouring_graph.png}}
        \caption{Illustration of a neighbouring graph.}
        \label{fig:neigh_graph}
    \end{figure}

@@

        Finally, informations about the technologies used in every site is provided. Indeed, a site can use multiple technologies.
        In Figure~\ref{fig:data_evolution} the evolution of each technology from the first updates of the data can be found.
        \begin{figure}
            \centering
            \boxed{\includegraphics[width=2.5in]{images/data_analysis/technos-evolution.png}}
            \caption{Evolution by quarter year and by technology of the number of \acrshort{bs}.}
            \label{fig:data_evolution}
        \end{figure}
        Then, in Figure~\ref{fig:data_technos} a chart showing the number of times each technology is present for each provider can be found.
        \begin{figure}
            \centering
            \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
            \caption{Breakdown, by operator, of the number of sites containing a given technology.}
            \label{fig:data_technos}
        \end{figure}
        We can see, for example, that \emph{Free Mobile} doesn't have any \acrshort{bs} with $2$G technology. Additionally, you can also find these values in Table~\ref{table:techno_numbers}.
        \begin{table}
            \centering
            \caption{Number of \acrshort{bs} equipped, at least, with $x$G, by provider.}
            \label{table:techno_numbers}
            \begin{tabular}{cccccc}
                \toprule
                \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
                \cmidrule(lr){1-6}
                \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
                \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
                \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
                \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
                \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
                \bottomrule
            \end{tabular}
        \end{table}

@@

            \begin{figure}
                \centering
                \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
                \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
                \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red).}
                \label{fig:del_tri}
            \end{figure}

@@

            The quadrant criterion is illustrated in Fig~\ref{fig:crit_qua}.
            \begin{figure}
                \centering
                \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
                \caption{Illustation of the rotated quadrant criterion.}
                \label{fig:crit_qua}
            \end{figure}

@@

        In the future, there will be method to compare our results with a reference. [pas sûr si on garde ca]
        \begin{figure}
            \centering
            \boxed{\includegraphics[width=2.5in]{images/illus_graphs/final_neighs_del_da.png}}
            \caption{The final neighbouring graph.}
            \label{fig:final_neighs}
        \end{figure}

>>>>

    Therefore, the outcome of the method presented is a neighbouring graph, cf. Figure~\ref{fig:neigh_graph}, where each node is a \acrshort{bs} and each edge represent a neighbouring relationship between these two \acrshort{bs}s.
    \begin{figure}
        \centering
        \includegraphics[width=3.5in]{images/illus_graphs/neighbouring_graph.png}
        \caption{Illustration of a neighbouring graph.}
        \label{fig:neigh_graph}
    \end{figure}

@@

        Finally, informations about the technologies used in every site is provided. Indeed, a site can use multiple technologies.
        In Figure~\ref{fig:data_evolution} the evolution of each technology from the first updates of the data can be found.
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/data_analysis/technos-evolution.png}
            \caption{Evolution by quarter year and by technology of the number of \acrshort{bs}.}
            \label{fig:data_evolution}
        \end{figure}
        Then, in Figure~\ref{fig:data_technos} a chart showing the number of times each technology is present for each provider can be found.
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/data_analysis/with_techno.png}
            \caption{Breakdown, by operator, of the number of sites containing a given technology.}
            \label{fig:data_technos}
        \end{figure}
        We can see, for example, that \emph{Free Mobile} doesn't have any \acrshort{bs} with $2$G technology. Additionally, you can also find these values in Table~\ref{table:techno_numbers}.
        \begin{table}
            \centering
            \caption{Number of \acrshort{bs} equipped, at least, with $x$G, by provider.}
            \label{table:techno_numbers}
            \begin{tabular}{cccccc}
                \toprule
                \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
                \cmidrule(lr){1-6}
                \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
                \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
                \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
                \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
                \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
                \bottomrule
            \end{tabular}
        \end{table}

@@

            \begin{figure}
                \centering
                \includegraphics[width=1.6in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}
                \includegraphics[width=1.6in]{images/illus_graphs/Delaunay_Voronoi.png}
                \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red).}
                \label{fig:del_tri}
            \end{figure}

@@

            The quadrant criterion is illustrated in Fig~\ref{fig:crit_qua}.
            \begin{figure}
                \centering
                \includegraphics[width=3.5in]{images/illus_crit/quadrant_elim.png}
                \caption{Illustation of the rotated quadrant criterion.}
                \label{fig:crit_qua}
            \end{figure}

@@

        In the future, there will be method to compare our results with a reference. [pas sûr si on garde ca]
        \begin{figure}
            \centering
            \includegraphics[width=3.5in]{images/illus_graphs/final_neighs_del_da.png}
            \caption{The final neighbouring graph.}
            \label{fig:final_neighs}
        \end{figure}
